Bayesian Evidence Synthesis:opioid crisis

### 2020-01-29 article_4/newpaper.tex
dynamic figure saving fixed and done...

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_under-ot.png}\label{under_ot}}
	\subfloat[ppc of $U_t$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_over-ot}\label{over_ot}}
	\caption[two early result box plots:]{Boxplot of posterior samples of $O_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $O_t$ values are shown as red dots.}
	\label{contam_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_under-ut.png}\label{under_ut}}
	\subfloat[ppc of $U_t$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_over-ut}\label{over_ut}}
	\caption[two early result box plots:ut]{Boxplot of posterior samples of $U_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $U_t$ values are shown as red dots.}
	\label{contam_ut}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $x_A$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_under-xa.png}\label{under_xa}}
	\subfloat[ppc of $x_A$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_over-xa}\label{over_xa}}
	\caption[two early result box plots:xa]{Boxplot of posterior samples of $x_A$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $x_A$ values are shown as red dots.}
	\label{contam_xt}
\end{figure}

>>>>

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $O_t$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-o_t.png}\label{under_ot}}
	\subfloat[ppc of $O_t$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-o_t}\label{over_ot}}
	\caption[two early result box plots:]{Boxplot of posterior samples of $O_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $O_t$ values are shown as red dots.}
	\label{contam_ot}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-u_t.png}\label{under_ut}}
	\subfloat[ppc of $U_t$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-u_t}\label{over_ut}}
	\caption[two early result box plots:ut]{Boxplot of posterior samples of $U_t$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $U_t$ values are shown as red dots.}
	\label{contam_ut}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\subfloat[ppc of $x_A$: underestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_underestimated-x_a.png}\label{under_xa}}
	\subfloat[ppc of $x_A$: overestimated $p_A$]{\includegraphics[width=.50\columnwidth]{early_contamination_overestimated-x_a.png}\label{over_xa}}
	\caption[two early result box plots:xa]{Boxplot of posterior samples of $x_A$ (1000 samples) where survey data is contaminated.  The actual data point of simulated $x_A$ values are shown as red dots.}
	\label{contam_xt}
\end{figure}
